---
title: 'Assignment: data.table'
author: "Owen Auston-Babcock and Bradley Collins"
date: "2025-03-02"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(data.table)
```

1. Use and show `data.table` code to select the variables `year`, `month`, `day`, and `hour` from the imported flights data

```{r}
flights14 <- fread("flights14.csv")
str(flights14)
flights14[, .(year, month, day, hour)]
```

2. Use and show `data.table` code to produce a table that shows a carrier of DL, an origin of JFK and a destination of SEA

```{r}
flights14[carrier=="DL" & origin=="JFK" & dest=="SEA"]
```

3. Use and show `data.table` code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}
flights14[carrier=="UA" & month==3 & air_time<330]
```

4. Use and show `tidyverse` code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}
flights14 %>% filter(carrier=="UA" & month==3 & air_time<330)
```

