---
title: 'Assignment: data.table'
author: "Owen Auston-Babcock and Bradley Collins"
date: "2025-03-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(data.table)

nycdata <- fread("nycdata.csv")
```

# Owen's section

## Question 1

Shows a table of year, month, day and hour from imported data (data.table)
```{r}
nycdata[, .(year, month, day, hour)]
```

## Question 2

Shows a table of DL flights from JFK to SEA (data.table)
```{r}
nycdata[carrier=="DL" & origin=="JFK" & dest=="SEA"]
```

## Question 3

Shows a table of DL flights in March that were under 330 minutes flight time (data.table)
```{r}
nycdata[carrier=="UA" & month==3 & air_time<330]
```

## Question 4

Shows a table of DL flights in March that were under 330 minutes flight time (tidyverse)
```{r}
nycdata %>% filter(carrier=="UA" & month==3 & air_time<330)
```

# Bradley's section

## Question 5

Calculates airspeed in miles per hour (data.table)
```{r}
nycdata[, speed := distance / (air_time/60)]
```

## Question 6

Calculates airspeed in miles per hour (tidyverse)
```{r}
nycdata <- nycdata %>% mutate(air_speed = distance/(air_time/60))
```

### Question 7

### 7a

Changes the abbreviation to UnitedAir using data.table
```{r}
nycdata[carrier == 'UA', carrier := "UnitedAir"]
```

### 7b

Changes the abbreviation to UnitedAir using tidyverse
```{r}
nycdata <- nycdata %>% mutate(carrier =ifelse(carrier =='UA','UnitedAir', carrier))
```

